Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-03 analysis/sim/run_simpw.Rmd
update sims

# Intro

@@

9. fgsea up gene sets

10. fgsea down gene sets

11. phyper up gene sets

12. phyper down gene sets

13. clusterprofiler_default up gene sets

14. clusterprofiler_default down gene sets

15. clusterprofiler_fixed up gene sets

16. clusterprofiler_fixed down gene sets

17. clusterprofiler_nobg up gene sets

18. clusterprofiler_nobg down gene sets

19. fisher up gene sets

20. fisher down gene sets

21. DOSE up gene sets

22. DOSE down gene sets

@@

# Session information

>>>>

## Intro

@@

9. clusterprofiler_default up gene sets

10. clusterprofiler_default down gene sets

11. clusterprofiler_fixed up gene sets

12. clusterprofiler_fixed down gene sets

13. clusterprofiler_nobg up gene sets

14. clusterprofiler_nobg down gene sets

15. fora up gene sets

16. fora down gene sets

17. fgsea up gene sets

18. fgsea down gene sets

@@

## Plot

```{r,plot1}

cp <- subset(res,PWAY_FUNC == "clusterprofiler")
fo <- subset(res,PWAY_FUNC == "fora")
fg <- subset(res,PWAY_FUNC == "fgsea")

par(mfrow=c(1,3))

plot(cp$VARIANCE,cp$p,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="precision")
points(fo$VARIANCE,fo$p,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$p,type="b",pch=19,col="blue")

legend("bottomleft", inset=.02, title="tool",
   c("clusterprofiler","fora","fgsea"), col=c("black","red","blue"), horiz=FALSE, cex=1.2, pch=19,lwd=2)

plot(cp$VARIANCE,cp$r,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="recall")
points(fo$VARIANCE,fo$r,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$r,type="b",pch=19,col="blue")

plot(cp$VARIANCE,cp$f,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="f1")
points(fo$VARIANCE,fo$f,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$f,type="b",pch=19,col="blue")

par(mfrow=c(1,1))

## Session information
